---
title: "BILGER-HANS-ADA-HOMEWORK-04"
author: "Hans Bilger"
date: "April 14, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### David Ledesma and I worked together on this homework assignment.

####Load in Kamilar and Cooper data
```{r}
library(readr)
d <- read_csv("KamilarAndCooper")
head(d)
```


####[1] Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).
```{r}

model <- lm(data=d, log(HomeRange_km2)~log(Body_mass_female_mean))
summary(model)
model$coefficients
coef(summary(model))[1,1]

# b0 (intercept) = -9.44
# b1 (slope) = 1.036

```

####[2] Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the appropriate coefficients. [The size of each sample should be equivalent to the number of observations in your dataset.] This generates a sampling distribution for each β coefficient. Plot a histogram of these sampling distributions.

```{r}
# b0 histogram
library(boot)
library(tidyverse)
s <- function(data,formula){  
	sim = sample_n(d, 213, replace = TRUE)
	return(lm(data=sim, log(HomeRange_km2)~log(Body_mass_female_mean))$coef[1])  
}
b0 <- boot(data=d, statistic=s, R=1000) 
hist(b0$t, breaks = 100)
```

```{r}
#b1 histogram
s <- function(data,formula){  
	sim = sample_n(d, 213, replace = TRUE)
	return(lm(data=sim, log(HomeRange_km2)~log(Body_mass_female_mean))$coef[2])  
	}
b1 <- boot(data=d, statistic=s, R=1000) 
hist(b1$t, breaks = 100)
```

####[3] Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap.
```{r}
# Standard error of b0
SE_b0_boot <- sd(b0$t)
SE_b0_boot
# Standard error of b1
SE_b1_boot <- sd(b1$t)
SE_b1_boot
```

#### [4] Also determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution.
```{r}
b0_CI_boot <- boot.ci(boot.out = b0, type = c("norm"))
b0_CI_boot
b1_CI_boot <- boot.ci(boot.out = b1, type = c("norm"))
b1_CI_boot
```
#### [5] How does your answer to part [3] compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?

```{r}
mod_1 <- lm(data=d, log(HomeRange_km2)~log(Body_mass_female_mean))
summary(mod_1)

SE_b1 <- .0849
SE_b1
SE_b1_boot
SE_b0 <- .673
SE_b0
SE_b0_boot

Pdiff_b1 <- 100*(1-SE_b1_boot/SE_b1)
Pdiff_b1
Pdiff_b0 <- 100*(1-SE_b0_boot/SE_b0)
Pdiff_b0

# The bootstrap Standard Errors are ~8-11% lower than the lm() Standard Errors.
```


#### [6] How does your answer to part [4] compare to the 95% CI estimated from your entire dataset?

```{r}
mod_1 <- lm(data=d, log(HomeRange_km2)~log(Body_mass_female_mean))
summary(mod_1)
confint(mod_1, 'log(Body_mass_female_mean)', level=0.95)
# Entire data set CI: 0.869, 1.204
# Bootstrap b1 CI =  0.859,  1.157 

PCIdiff <- 100*(1-(1.157-.859)/(1.204-.869))
PCIdiff

# So the bootstrapped 95% CI is ~11% smaller than the 95% CI from the entire dataset. 
```
#### EXTRA CREDIT: + 2
Write a FUNCTION that takes as its arguments a dataframe (“d”), a linear model (“m”, as a character string, e.g., “logHR~logBM”), a user-defined confidence interval level (“conf.level”) with default = 0.95, and a number of bootstrap replicates (“n”, with default = 1000). Your function should return a dataframe that includes: beta coefficient names; beta coefficients, standard errors, and upper and lower CI limits for the linear model based on your entire dataset; and mean beta coefficient estimates, SEs, and CI limits for those coefficients based on your bootstrap.

##### Below is our attempt at EXTRA CREDIT +2. We couldn't get the function to work, but the code below shows our line of thinking.

```{r, eval=FALSE}
frog <- function(x, m, conf.level=0.95, n=1000){
    b1 <- lm(data=x, m)$coef[2] 
    b0 <- lm(data=x m)$coef[1]
    SE_b0 <- summary(lm(m))$coef[3]
    SE_b1 <- summary(lm(m))$coef[4]
    CI_low <- confint(m, level=conf.level)[[1]]
    CI_up <- confint(m, level=conf.level)[[2]]
      library(boot)
      s <- function(data,formula){  
    	sim = sample_n(d, nrow(x), replace = TRUE)
	    return(lm(data=sim, log(HomeRange_km2)~log(Body_mass_female_mean))$coef[1])  
    	}
      b0_b00t <- boot(data=sim, statistic=s, R=n)
      SE_b0_b00tt <- sd(b0_b00t$t)
      b0_CI_b00t <- boot.ci(boot.out = b0_b00t, type = c("norm"))
      meanb0 <- mean(b0_b00t$t)
        t <- function(data,formula){  
    	  sim = sample_n(d, nrow(x), replace = TRUE)
	      return(lm(data=sim, log(HomeRange_km2)~log(Body_mass_female_mean))$coef[2])  
      	}
        b1_b00t <- boot(data=sim, statistic=t, R=n)
        meanb1 <- mean(b1_b00t$t)
        SE_b1_b00tt <- sd(b1_b00t$t)
        b1_CI_b00t <- boot.ci(boot.out = b1_b00t, type = c("norm"))
        values <- data.frame(b1 = b1, b0 = b0, 'SE of b0' = SE_b0, 'SE of b1' = SE_b1, CI_low = CI_low, CI_up = CI_up, 'b0 bootstrap' = b0_b00t, 'SE b0 bootstrap' = SE_b0_b00t, 'CI b0 bootstrap' = b0_CI_b00t, 'b1 bootstrap' = b1_b00t, 'SE b1 bootstrap' = SE_b1_b00t, 'CI b1 bootstrap' = b1_CI_b00t)
        return(values)
      
frog(, 'd$log(HomeRange_km2)~d$log(Body_mass_female_mean)')
    
lm(d, log(HomeRange_km2)~log(Body_mass_female_mean))
}
summary(lm(data=sim, log(HomeRange_km2)~log(Body_mass_female_mean)))
summary(lm(data=sim, log(HomeRange_km2)~log(Body_mass_female_mean)))$coef[3]
s <- function(data,b,formula){  
	sim = sample_n(d, 213, replace = TRUE)
	return(lm(data=sim, log(HomeRange_km2)~log(Body_mass_female_mean))$coef[2])  
	}
b1 <- boot(data=sim, statistic=s, R=1000) 
```
